Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-08-29 Phase_II/draft/AJsubmitted/main.tex
setting up redblue wrt AJ submitted

\documentclass[twocolumn]{emulateapj}

\usepackage{amsmath}
\usepackage[colorlinks=true,
linkcolor=blue,
citecolor=blue,
urlcolor=cyan]{hyperref}

@@

\title{Generative AI for image reconstruction\\ in Intensity Interferometry: a first attempt}

\author{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen
  Basak$^{1}$, Prasenjit Saha$^{3}$, and Subrata Sarangi$^{4,5}$}

\affiliation{$^{1}$School of Physics, Indian Institute of Science
  Education and Research Thiruvananthapuram, Maruthamala PO, Vithura,
  Thiruvananthapuram 695551, Kerala, India.}

\affiliation{$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.}

\affiliation{$^{3}$Physik-Institut, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland.}

\affiliation{$^{4}$School of Applied Sciences, Centurion University of
  Technology and Management, Odisha-752050, India.}

\affiliation{$^5$ Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}

@@

\maketitle

@@

\bibliographystyle{aa}
\bibliography{refs}

>>>>

\documentclass[linenumbers, twocolumn]{aastex701}
\usepackage{amsmath}

@@

\title{Generative AI for image reconstruction in Intensity Interferometry: a first attempt}

\author{Km Nitu Rai}
\affiliation{School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO, Vithura, Thiruvananthapuram 695551, Kerala, India.}
\affiliation{Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.}
\email{niturai201296@gmail.com}

\author{Yuri van der Burg} 
\affiliation{Physik-Institut, University of Zurich,	Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
\email{yuri.vanderburg@uzh.ch}

\author{Soumen Basak}
\affiliation{School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO, Vithura, Thiruvananthapuram 695551, Kerala, India.}
\email{sbasak2006@gmail.com}

\author{Prasenjit Saha}
\affiliation{Physik-Institut, University of Zurich,	Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
\email{psaha@physik.uzh.ch}

\author{Subrata Sarangi}
\affiliation{School of Applied Sciences, Centurion University of	Technology and Management, Odisha-752050, India.}
\affiliation{Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}
\email{ssarangi.itech@gmail.com}

@@

@@

\bibliographystyle{aasjournalv7}
\bibliography{refs}
